Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and correlation with baryon disk properties

### 2019-07-15 Document/paper.tex
edit

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.png}
 \includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.png}
\end{center}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
  on the left and MHD simulations on the right.
   Each dot represents the shape characterization of each halo 
   Red circles represent measurements at the virial radius and the
   blue squares are measurements at 1/8 of the virial radius.   
   The crosses represent the mean values and standard deviation of
   each sample.
   Overall we can see three things. 
   First, in DM only simulations halos are rounder in the outskirts
   than in the inner part.
   Second, halos in MHD are rounder than its DM only counterparts.
   Third, halos in MHD simulations are slightly rounder in the inner
   part compared to the outskirts.}
  \label{fig:triaxiality_plane}
\end{figure*}

@@

The DM halo shape at a fixed radius is an estimate of either
the isopotential or isodensity surfaces.  
Observational inference models usually estimate the 
isopotential contours which are probed by tracers (gas, stars), while
simulations work with the isodensity contours which can be directly
calculated from particle positions.  
Furthermore, the density contours in thin shells are very sensitive to
the presence of small satelites.  
For this reason we measure the shape by taking
volume-enclosed particles, rather than shell-enclosed.

@@

where the particle positions are measured from the minimum of the
gravitational potential in each halo and each is weighted by the k-th
particle distance 
$d_k^2=x_k^2+y_k^2+z_k^2$,

@@

Next we want to test to what extend the global effect of decreasing
triaxility in MHD simulations compared to the DMO sample 
holds for individual halos. 
We compute $\Delta_T\equiv T_{MHD}-T_{DMO}$ the difference between the
triaxility in the MHD and the DMO simulation for each individual halo. 
Figure \label{fig:delta_triaxial_cumulative} shows the cumulative
distribution at the same radii as in
Figure \label{fig:delta_triaxial_cumulative}.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_DM.pdf}
 \includegraphics[width=0.9\columnwidth]{Lvl_4_Triax_Plane_MHD.pdf}
\end{center}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations
  on the left and MHD simulations on the right.
   Each dot represents the shape characterization of each halo 
   Red circles represent measurements at the virial radius and the
   blue squares are measurements at 1/8 of the virial radius.   
   The crosses represent the mean values and standard deviation of
   each sample.
   Overall we can see three things. 
   First, in DM only simulations halos are rounder in the outskirts
   than in the inner part.
   Second, halos in MHD are rounder than its DM only counterparts.
   Third, halos in MHD simulations are slightly rounder in the inner
   part compared to the outskirts.}
  \label{fig:triaxiality_plane}
\end{figure*}

@@

The DM halo shape at a fixed radius is an estimate of either
the isopotential or isodensity surfaces.  
Observational inference models usually estimate the 
isopotential contours which are probed by tracers (gas, stars), while
simulations work with the isodensity contours which can be directly
calculated from particle positions.  
Furthermore, the density contours in thin shells are very sensitive to
the presence of small satelites.  
For this reason we measure the shape by taking
volume-enclosed particles, rather than shell-enclosed.  
This method yields results in good agreement to the isodensity
contours for radii smaller than half the virial radius as explored by
\citep{Vera-Ciro_et_al._2011}.

@@

where the particle positions are measured from the minimum of the
gravitational potential in each halo and each is weighted by the k-th
particle distance 
$d_k^2=x_k^2+y_k^2+z_k^2$.

@@

Next we want to test to what extend the global effect of decreasing
triaxility in MHD simulations compared to the DMO sample 
holds for individual halos. 
We compute $\Delta T\equiv T_{\rm MHD}-T_{\rm DMO}$ the difference between the
triaxility in the MHD and the DMO simulation for each individual halo. 
Figure \label{fig:delta_triaxial_cumulative} shows the cumulative
distribution at the same radii as in
Figure \label{fig:delta_triaxial_cumulative}.
